\mutagen: Reliable Coverage-Guided, Property-Based Testing using Exhaustive Well-Typed Mutations

### 2021-04-05 papers/oopsla-21/main.tex
WIO
WIP

\begin{algorithm}[H]
  \SetArgSty{textnormal}
  \SetInd{0em}{0.75em}
  \SetKw{KwNot}{not}
  \SetAlgoLined
  \DontPrintSemicolon
  \SetKwFunction{FC}{Loop}
  \SetKwProg{Fn}{Function}{:}{}
  \Fn{\FC{P, N, gen, mut}}{
    i $\gets$ 0\;
    TLog, QSucc, QDisc $\gets$ $\varnothing$;\;
    \While{i $<$ N}{
      x $\gets$ Pick(QSucc, QDisc, gen, mut)\;
      (result, trace) $\gets$ WithTrace(P(x))\;
      \lIf{\KwNot result}{\KwRet Bug(x)}
      \If{Interesting(TLog, trace)}{
        e $\gets$ Energy(TLog, x, trace)\;
        \eIf{\KwNot Discarded(result)}{
          Enqueue(QSucc, (x, e))\;
        }{
          Enqueue(QDisc, (x, e))\;
        }
      }
      i $\gets$ i+1\;
    }
    \KwRet Ok\;
  }
\caption{\label{algo:fuzzchick:loop}\fuzzchick Testing Loop}
\end{algorithm}

@@

\begin{figure}
\begin{verbatim}
mutate_tree :: (a -> Gen a) -> Tree a -> Gen (Tree a)
mutate_tree mutate_a (Leaf x) =
  oneof [ do { x' <- mutate_a x; return (Leaf x')}                     -- Mutate recursively
        , do { l <- arbitrary; r <- arbitrary; return (Node l x r) } ] -- Grow constructor
mutate_tree (Node l x r) =
  oneof [ return l                                                     -- Return subexpression
        , return r                                                     -- Return subexpression
        , return (Leaf x)                                              -- Shrink constructor
        , do { l' <- mutate_tree l; return (Node l' x r) }             -- Mutate recursively
        , do { x' <- mutate_a    x; return (Node l x' r) }             -- Mutate recursively
        , do { r' <- mutate_tree r; return (Node l x r') } ]           -- Mutate recursively
\end{verbatim}
\caption{\label{fig:fuzzchick:mutator}\fuzzchick mutator for the \texttt{Tree} data type. }
\end{figure}

@@

\begin{algorithm}[H]
  \SetArgSty{textnormal}
  \SetInd{0em}{0.75em}
  \SetKw{KwNot}{not}
  \SetAlgoLined
  \DontPrintSemicolon
  \SetKwFunction{MG}{Loop}
  \SetKwProg{Fn}{Function}{:}{}
  \Fn{\MG{P, N, R, gen, mut}}{
    i $\gets$ 0\;
    TLog, QSucc, QDisc $\gets$ $\varnothing$;\;
    \While{i $<$ N}{
      x $\gets$ Pick(QSucc, QDisc, gen, mut)\;
      (result, trace) $\gets$ WithTrace(P(x))\;
      \lIf{\KwNot result}{\KwRet Bug(x)}
      \If{Interesting(TLog, trace)}{
        \If{\KwNot Discarded(result)}{
          muts $\gets$ Mutants(x, mut, R)\;
          Enqueue(QSucc, muts)\;
        }
        \uElseIf{Passed(Parent(x))}{
          muts $\gets$ Mutate(x, mut, R)\;
          Enqueue(QDisc, muts)\;
        }
      }
      i $\gets$ i+1\;
    }
    \KwRet Ok\;
  }
\caption{\label{algo:mutagen:loop}\mutagen Testing Loop}
\end{algorithm}

>>>>

\begin{algorithm}[H]
  \SetArgSty{textnormal}
  \SetInd{0em}{0.75em}
  \SetKw{KwNot}{not}
  \SetAlgoLined
  \DontPrintSemicolon
  \SetKwFunction{FC}{Loop}
  \SetKwProg{Fn}{Function}{:}{}
  \Fn{\FC{P, N, gen, mut}}{
    i $\gets$ 0\;
    TLog, QSucc, QDisc $\gets$ $\varnothing$\;
    \While{i $<$ N}{
      x $\gets$ Pick(QSucc, QDisc, gen, mut)\;
      (result, trace) $\gets$ WithTrace(P(x))\;
      \lIf{\KwNot result}{\KwRet Bug(x)}
      \If{Interesting(TLog, trace)}{
        e $\gets$ Energy(TLog, x, trace)\;
        \eIf{\KwNot Discarded(result)}{
          Enqueue(QSucc, (x, e))\;
        }{
          Enqueue(QDisc, (x, e))\;
        }
      }
      i $\gets$ i+1\;
    }
    \KwRet Ok\;
  }
\caption{\label{algo:fuzzchick:loop}\fuzzchick Testing Loop}
\end{algorithm}

@@

\begin{figure}
\begin{verbatim}
mutate_tree :: (a -> Gen a) -> Tree a -> Gen (Tree a)
mutate_tree mutate_a (Leaf x) =
  oneof [ do { x' <- mutate_a x; return (Leaf x')}                     -- Mutate recursively
        , do { l <- arbitrary; r <- arbitrary; return (Node l x r) } ] -- Grow constructor
mutate_tree mutate_a (Node l x r) =
  oneof [ return l                                                     -- Return subexpression
        , return r                                                     -- Return subexpression
        , return (Leaf x)                                              -- Shrink constructor
        , do { l' <- mutate_tree l; return (Node l' x r) }             -- Mutate recursively
        , do { x' <- mutate_a    x; return (Node l x' r) }             -- Mutate recursively
        , do { r' <- mutate_tree r; return (Node l x r') } ]           -- Mutate recursively
\end{verbatim}
\caption{\label{fig:fuzzchick:mutator}\fuzzchick mutator for the \texttt{Tree} data type. }
\end{figure}

@@

\begin{algorithm}[H]
  \SetArgSty{textnormal}
  \SetInd{0em}{0.75em}
  \SetKw{KwNot}{not}
  \SetAlgoLined
  \DontPrintSemicolon
  \SetKwFunction{MG}{Loop}
  \SetKwProg{Fn}{Function}{:}{}
  \Fn{\MG{P, N, R, gen, mut}}{
    i $\gets$ 0\;
    TLog, QSucc, QDisc $\gets$ $\varnothing$\;
    \While{i $<$ N}{
      x $\gets$ Pick(QSucc, QDisc, gen)\;
      (result, trace) $\gets$ WithTrace(P(x))\;
      \lIf{\KwNot result}{\KwRet Bug(x)}
      \If{Interesting(TLog, trace)}{
        \If{\KwNot Discarded(result)}{
          muts $\gets$ Mutate(x, mut, R)\;
          Enqueue(QSucc, muts)\;
        }
        \uElseIf{Passed(Parent(x))}{
          muts $\gets$ Mutate(x, mut, R)\;
          Enqueue(QDisc, muts)\;
        }
      }
      i $\gets$ i+1\;
    }
    \KwRet Ok\;
  }
\caption{\label{algo:mutagen:loop}\mutagen Testing Loop}
\end{algorithm}
